### 2015-11-26 Manuscript/BiologyLetters/CoverLetter.tex
small comment on cover letter

Please find attached our research article, ``Assessment of cladistic data availability for living mammals'', for consideration in the Biology Letters Special Issue: % NC: What is the title?

>>>>

Please find attached our research article, ``Assessment of cladistic data availability for living mammals'', for consideration in the Biology Letters Special Issue: ``Putting fossils into trees''.% NC: What is the title?
%TG: TO CHECK
